PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2023-01-17 main.tex
Fix grant number in acknowledgements

\section*{Acknowledgements}
The simulations presented in this work were run on XSEDE/SDSC Comet and Expanse under allocation MCA94P018. SCW and TRQ were were supported by NSF award 62-2684. We acknowledge the people of the Dkhw’Duw’Absh, the Duwamish Tribe, the Muckleshoot Tribe, and other tribes on whose traditional lands we have performed this work.

>>>>

\section*{Acknowledgements}
This work used the Extreme Science and Engineering Discovery Environment (XSEDE), which is supported by National Science Foundation grant number ACI-1548562. SCW and TRQ were were supported by National Science Foundation grant number AST-2006752. We acknowledge the people of the Dkhw’Duw’Absh, the Duwamish Tribe, the Muckleshoot Tribe, and other tribes on whose traditional lands we have performed this work.
